---
title: "rsellTables"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Version 1.0.0

Base functions for creating tables used within the R-Sell App.

## Installation

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("t2tech-corp/Rsell-Packages", subdir = "rsellTables")
```


## Usage

Package loaded from the **global.R** file in the Shiny App.

## Link

Package location in Github: [rsell](https://github.com/t2tech-corp/Rsell-Packages/tree/main/rsellTables)

## List of Functions

1. Cash_Flow_Summary
2. Create_YM_Inventory_Added_Summary
3. Create_YM_Inventory_Sell_Through
4. Create_YM_Inventory_sold_Summary
5. Create_YM_Sales_Summary
6. Create_YM_Table
7. Create_YW_Cash_Flow_Cum
8. Create_YW_Cash_Flow_In
9. Create_YW_Cash_Flow_Out
10. Create_YW_Table
11. Daily_Sales_Summary
12. Inv_Bin_Summary
13. Inv_Bin_Table
14. Inventory_Summary_Listed
15. Inventory_Summary_Open
16. Inventory_Summary_Sold
17. Inventory_Summary_Total
18. Merch_Sales_Summary
19. Monthly_Inventory_Detail
20. Monthly_Inventory_Sell_Through
21. Monthly_Sales_Detail
22. Monthly_Sales_Summary
