---
title: "rsellTables"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Version 1.0.0

Base functions for creating tables used within the R-Sell App.

## Installation

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("t2tech-corp/Rsell-Packages", subdir = "rsellTables")
```


## Usage

Package loaded from the **global.R** file in the Shiny App.

## Link

Package location in Github: [rsell](https://github.com/t2tech-corp/Rsell-Packages/tree/main/rsellTables)

## List of Functions

1. Cash_Flow_Summary
2. Daily_Sales_Summary
3. Inv_Bin_Summary
4. Inv_Bin_Table
5. Listed_Inventory_Summary
6. Merch_Sales_Summary
7. Monthly_Inventory_Detail
8. Monthly_Inventory_Summary
9. Monthly_Sales_Detail
10. Monthly_Sales_Summary
11. Open_Inventory_Summary
12. PM_Monthly_Activity
13. PM_Sales_Monthly
14. PM_Sales_Summary
15. PM_Summary_For_Chart
16. PM_Summary_Stats
17. PM_Summary_Stats_Conf
18. PM_Var_Summary
19. Sold_Inventory_Summary
20. Source_Inventory_Summary
21. Total_Inventory_Summary

