---
title: "rsellPoshmark"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Version 1.0.0

Base functions for Poshmark processing in R-Sell App.

## Installation

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("t2tech-corp/Rsell-Packages", subdir = "rsellPoshmark")
```


## Usage

Package loaded from the **global.R** file in the Shiny App.

## Link

Package location in Github: [rsell](https://github.com/t2tech-corp/Rsell-Packages/tree/main/rsellPoshmark)

## List of Functions

1. PM_Bar_Charts
2. PM_DT_Sales_Activity_Table
3. PM_DT_Summary_Table
4. PM_Sales_Table_Delete_Record
5. PM_Sales_Table_Sort
6. PM_Sales_Upload_Blank_SKU
7. PM_Sales_Upload_Format_Confirm
8. PM_Sales_Upload_Format_Summary
9. PM_Sales_Upload_Item_Cost
10. PM_Sales_Upload_Partial_SKU
11. PM_Sales_Upload_Process
12. PM_Sales_Upload_Submit
13. PM_Sales_Upload_Summary_Stats
14. PM_Sales_Upload_Update_Inventory
15. PM_Sales_Upload_Validate
16. PM_Table_Monthly_Activate
17. PM_Table_Sales_Monthly
18. PM_Table_Sales_Summary
19. PM_Table_Summary_For_Chart
20. PM_Table_Summary_Stats_Conf
21. PM_Table_Var_Summary

